---
title: "Literature Network"
author: "Whitney Friedman"
date: "11/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##Randomly select citations
pacman::p_load(rio,rcrossref,bib2df,tidytext,revtools,fuzzyjoin,igraph,ggraph,janitor,tidyverse)

workdir <- "R:/Gill/research/oegm/"
#workdir <- gsub("git","data",getwd())
inputdir <- paste0(workdir,"tables/raw/Cons-HWB-citations-from-reviews/")
outputdir <- paste0(workdir,"output/tables/")
plotdir <- paste0(workdir,"output/plots/")
today.date <- gsub("-","",Sys.Date())
list.files(inputdir)
last.file <- function(dir.nam,nam){
  import(paste0(dir.nam,last(sort(grep(nam,list.files(dir.nam), value=T)))))
}

```

# Literature overlap network
This RMD demonstrates how the literature overlap network used in the OECM meta-review was created. 

## Prior work
In order to create this network, lists of references were extracted from the 
supplementary materials for the 7 studies included in the OECM meta-review. This
was an ugly process involving PDF scanning, some manual formatting, and google docs. 
This document picks up from the formatted and combined version of that work. 

Note that I did not attempt to format the full citation. I simply extracted the 
first author and year from each citation and then manually double checked to make sure that any 
duplicate author_year values were given a unique code (a,b,c...) when there were multiple papers 
by that first author in a given year.

## Read file of combined refs

```{r}

file.list <- list.files(inputdir,full.names = T)
tmp <- read_bibliography(file.list[42]) 
file.list <- file.list[-42]
wanted.var <- c("label","type","title","author","year","keywords","journal","doi","abstract")
names(tmp)names(wanted.var)
r.data <- data.frame()

for (i in 1:length(file.list)){
study_id <- gsub(inputdir,"",file.list[i],file.list[i])
tmp <- read_bibliography(file.list[i])  %>% 
  mutate(study_id=gsub(".ris","",study_id))
r.data <- bind_rows(r.data,tmp)
print(i)
}

sapply(r.data, function(x) sum(is.na(x))/length(x))
table(r.data$study_id)

refs_reviewed <- r.data %>% 
 select(label,type,title,author,year,keywords,journal,doi,abstract,study_id) %>% 
  mutate(first_author=sub("\\,.*", "", author),
         author_year=str_c(first_author,year,sep = " ")) %>% 
  mutate(across(c(title,abstract),list(z=~replace_na(.,"")))) %>%  # replace NAs with "" (for combining strings)
  mutate(across(c(title_z,abstract_z),~str_to_lower(.))) %>%   # lower case
  mutate(across(c(title_z,abstract_z),~str_replace_all(.,"\\W", ""))) 

head(select(refs_reviewed,author,first_author,author_year))

```

## List studies that are cited in multiple review papers

```{r}
# Studies cited in multiple reviews:
refs_overlap <- refs_reviewed %>% 
  get_dupes(label)

#refs_overlap %>% view

refs_overlap_short <- refs_overlap %>% 
  distinct(label,.keep_all = T) %>% 
  select(label,title,author,year,title_z, study_id) # No longer unique to the values

# 493 unique studies are contained in the 6 reviews. 
# Of those, 43 studies are repeated across the 6 reviews
# 43/493 = 0.0872211
#refs_overlap_short %>% view

```


## Network of overlapping studies
Helpful tutorials: 
https://cbail.github.io/ids704/social-networks/Intro_to_Network_Analysis_in_R.html
https://www.data-imaginist.com/2017/ggraph-introduction-layouts/

Only 2 columns are necessary: 
- "from" will be mapped to "study_id" (one of the 7 review papers)
- "to" will be mapped to "author_year" (one of the 493 studies cited by the review papers)

```{r}

refs_network <- refs_reviewed %>% 
  mutate(from = study_id, 
         to = label) %>% 
  select(from, to, study_id)

refs_network <- graph_from_data_frame(refs_network)

# Add degree (# of connections to each node; here, # of review citing each study)
V(refs_network)$degree<-degree(refs_network)


# Display networks

# This one is cool but uninformative
# ggraph(refs_network, layout = 'linear', circular = T) + 
#     geom_edge_arc(aes(colour = study_id)) +
#     geom_node_point()

# BEST
# see optional params: ?layout_with_fr
# Re-run this until happy with the information quality of the layout.
E(refs_network)$weight <- 1 # Assign weight

g<- ggraph(refs_network, layout = 'kk', niter=5000, weights = weight)+
    geom_edge_link(aes(colour = study_id)) +
    geom_node_point() 
    geom_node_label(aes(label = study_id), repel = TRUE)
g + theme(legend.position = "none")

# Keep the final iteration
g_best <- g 

# Save as PNG
png(paste0(plotdir,"refs_overlap_network_test_all_alt.png"),
    width=15, height = 9, units = "in", bg = "white", res = 300)
g_best
dev.off()

```