---
title: "OEGM script"
author: "David A. Gill & Dana I. Grieco"
date: "12/18/2020"
output: html_document
---

# Setup
Loads libraries, reads in data, cleans datasets
```{r eval=T}
#set working directory to the correct folders on your machine
workdir <- "R:/Gill/research/oegm/"
inputdir <- paste0(workdir,"tables/raw/")
mapdir <-  paste0(workdir,"spatial/raw/")
plotdir <- paste0(workdir,"output/plots/")

pacman::p_load(rio,rgeos,treemap,gtools,cowplot,rnaturalearth,rnaturalearthdata,tidyverse)

today.date <- gsub("-","",Sys.Date())

#--- Organize data ----
#read in data, skip first 2 rows
# non.mangrove<-import(paste0(inputdir,"Non-mangrove_FINAL.xlsx"), which="Data Extraction Sheet", skip =2, .name_repair = "universal") %>% 
#   mutate(Date=as.character(Date))
# mangrove<-import(paste0(inputdir,"Mangrove_FINAL.xlsx"), which="Data Extraction Sheet", skip =2,  .name_repair = "universal") %>% 
#   mutate(Date=as.character(Date))

all.data<-import(paste0(inputdir,"20191022_All Data.xlsx"), skip =2, .name_repair = "universal") %>% 
  mutate(Date=as.character(Date))
country <- import(paste0(inputdir,"allcountries.csv"))

# Count total papers in Full Text Screening
length(unique(all.data$Article.ID))

# Select accepted papers, rename variables==
data_all <- all.data %>%  
  filter(Full.text.screening.=="Accept" & !is.na(Intervention.category) & !is.na(Outcome.category)) %>% # is this ok to do? would be there cases where NA is ok?
  rename(Int_cat=Intervention.category,Outcome_cat=Outcome.category, aid=Article.ID, study.ctry=Country.ies..of.study)
length(unique(data_all$aid))

# read in full intervention lists
int_list<-import(paste0(inputdir,"intervention abbreviations.csv"))
out_list<-import(paste0(inputdir,"outcome abbreviations.csv"))
drop.down.lists<-import(paste0(inputdir,"20191022_All Data.xlsx"), which="Dropdowns", skip =1, .name_repair = "universal")

int_sub_list <-  drop.down.lists %>% 
  select(Intervention.subcategory) %>% 
  na.omit() %>% 
  rename(int_sub=Intervention.subcategory)
out_sub_list <-  drop.down.lists %>% 
  select(Outcome.subcategory) %>% 
  na.omit() %>% 
  rename(out_sub=Outcome.subcategory) 
num.studies <- length(unique(data_all$aid))


#--- Clean up data ----
# Something went wrong? shift over rows that were missing a column so the data shifted (aid=772), inspect in original data
data_all[data_all$aid%in%772,32:42] # wrong
data_all[data_all$aid%in%772,32:42]  <- data_all[data_all$aid%in%772,31:41] 
data_all[data_all$aid%in%772,32:42]  # right

# Recodes intervention and outcomes fields to the correct version 
# interventions
for (i in 1:nrow(int_list)){
  num.val=paste0("^",i,"\\. *") # starts with this number
  data_all <- data_all %>% 
    mutate(Int_cat=ifelse(grepl(num.val,Int_cat),grep(num.val,int_list$Int_cat_orig,value = T),Int_cat))
}
# sub-interventions
for (i in 1:nrow(int_sub_list)){
  num.val=paste0("^",gsub("\\.(.*)","",int_sub_list$int_sub[i]))  # starts with this number
  data_all <- data_all %>% 
    mutate(Intervention.subcategory=ifelse(grepl(num.val,Intervention.subcategory),
                                           grep(num.val,int_sub_list$int_sub,value = T),Intervention.subcategory))
}
# Outcomes
for (i in 1:nrow(out_list)){
  num.val=paste0("^",i)
  data_all <- data_all %>% 
    mutate(Outcome_cat=ifelse(grepl(num.val,Outcome_cat),grep(num.val,out_list$Outcome_cat_orig,value = T),Outcome_cat))
}
# Sub-outcomes
for (i in 1:nrow(out_sub_list)){
  num.val=paste0("^",gsub("\\.(.*)","",out_sub_list$out_sub[i]))  # starts with this number
  data_all <- data_all %>% 
    mutate(Outcome.subcategory=ifelse(grepl(num.val,Outcome.subcategory),
                                           grep(num.val,out_sub_list$out_sub,value = T),Outcome.subcategory))
}

#quick checks
unique(data_all$Int_cat)  # 10 interventions
unique(data_all$Outcome_cat) # 7 outcomes
sort(unique(data_all$Intervention.subcategory)) # 36 sub-interventions?
sort(unique(data_all$Outcome.subcategory)) # 41 sub-outcomes?

# those that were not observed
int_list$Int_cat_orig[!int_list$Int_cat_orig%in%data_all$Int_cat] 
int_sub_list$int_sub[!int_sub_list$int_sub%in%data_all$Intervention.subcategory] 
out_list$Outcome_cat_orig[!out_list$Outcome_cat_orig%in%data_all$Outcome_cat] 
out_sub_list$out_sub[!out_sub_list$out_sub%in%data_all$Outcome.subcategory] 

# incorrect values entered (all should be zero)  !Morgan: Intervention.subcategory with an NA
data_all$Int_cat[!data_all$Int_cat%in%int_list$Int_cat_orig] 
data_all$Intervention.subcategory[!data_all$Intervention.subcategory%in%int_sub_list$int_sub] 
data_all$Outcome_cat[!data_all$Outcome_cat%in%out_list$Outcome_cat_orig] 
data_all$Outcome.subcategory[!data_all$Outcome.subcategory%in%out_sub_list$out_sub] 

# Add habitat fields
unique(data_all$Habitat.type) 
data_all <- data_all %>% 
mutate(coral=ifelse(grepl("Coral",Habitat.type,ignore.case = T),1,0),
       seagrass=ifelse(grepl("Seagrass",Habitat.type,ignore.case = T),1,0),
       mangrove=ifelse(grepl("mangrove",Habitat.type,ignore.case = T),1,0),)

  # check habitat coding
unique(data_all$Habitat.type[data_all$coral==1])
unique(data_all$Habitat.type[data_all$seagrass==1])
unique(data_all$Habitat.type[data_all$mangrove==1])

habitat.test <- data_all %>% 
  filter(coral==0 & mangrove==0 & seagrass==0) %>% 
  select(Habitat.type)
unique(habitat.test$Habitat.type) # should just be "other"

# remove research and monitoring, and adjust numbers
data_all <-data_all %>% 
  filter(Int_cat!="8. Research & monitoring")%>% 
  mutate_at(vars(Int_cat,Intervention.subcategory), ~gsub("^9","8",.)) %>% 
  mutate_at(vars(Int_cat,Intervention.subcategory), ~gsub("^10","9",.)) %>% 
  mutate_at(vars(Outcome_cat,Outcome.subcategory), ~gsub("^1","9",.)) %>% 
  mutate_at(vars(Outcome_cat,Outcome.subcategory), ~gsub("^2","1",.)) %>% 
  mutate_at(vars(Outcome_cat,Outcome.subcategory), ~gsub("^3","2",.)) %>% 
  mutate_at(vars(Outcome_cat,Outcome.subcategory), ~gsub("^4","3",.)) %>% 
  mutate_at(vars(Outcome_cat,Outcome.subcategory), ~gsub("^5","4",.)) %>% 
  mutate_at(vars(Outcome_cat,Outcome.subcategory), ~gsub("^6","5",.)) %>% 
  mutate_at(vars(Outcome_cat,Outcome.subcategory), ~gsub("^9","6",.)) 

#new quick checks
unique(data_all$Int_cat)  # 9 interventions
unique(data_all$Outcome_cat) # 7 outcomes
sort(unique(data_all$Intervention.subcategory)) # 34 sub-interventions?
sort(unique(data_all$Outcome.subcategory)) # 41 sub-outcomes?

# # Get full intervention list
  int_list <- data_all %>%
    ungroup() %>%
    distinct(Int_cat) %>%
    rename(int_val=Int_cat) %>% 
    arrange(int_val)
  out_list <- data_all %>%
    ungroup() %>%
    distinct(Outcome_cat) %>%
    rename(out_val=Outcome_cat) %>% 
    arrange(out_val)
# Get full sub-intervention list
  int_sub_list <- data_all %>%
    ungroup() %>%
    distinct(Intervention.subcategory) %>%
    rename(int_val=Intervention.subcategory) %>% 
    arrange(int_val)
  out_sub_list <- data_all %>%
    ungroup() %>%
    distinct(Outcome.subcategory) %>%
    rename(out_val=Outcome.subcategory) %>% 
    arrange(out_val)

```


# Heat map function
Creates a heat map from the OESM accepted articles, based on intervention and outcome categories and subcategories
```{r eval=T}
#--- Heat map function ----
my_heat_map <- function (.data,intc, outc, high.col="#2171b5") {
  
  
# don't know why... but this works
  .data$intc<- as.vector(.data %>%  pull(intc))
  .data$outc<- as.vector(.data %>%  pull(outc))

# Set full intervention list type  
if(intc=="Int_cat"){int_list_full=int_list}
if(intc=="Intervention.subcategory"){int_list_full=int_sub_list}
if(outc=="Outcome_cat"){out_list_full=out_list}
if(outc=="Outcome.subcategory"){out_list_full=out_sub_list}

# Get unique article ID, int. and out. list (and sum of articles)
  typology_dat <- .data %>% 
    select(aid, intc, outc) %>% 
    filter(intc!="" & !is.na(intc)) %>%  # just in case
    distinct() %>% 
    full_join(int_list_full,by =c("intc"="int_val")) %>% 
    full_join(out_list_full,by =c("outc"="out_val")) %>% 
    group_by(intc) %>% 
    mutate(int_val=paste0(intc," (",n_distinct(aid,na.rm = T),")")) %>% 
    group_by(outc) %>% 
    mutate(out_val=paste0(outc," (",n_distinct(aid,na.rm = T),")")) %>% 
    ungroup() %>% 
    select(-c(intc,outc)) 
  
  # Get expanded intervention-outcome list for this dataset
  int_list <- typology_dat %>%
    ungroup() %>%
    filter(int_val!="NA (0)") %>% 
    distinct(int_val) %>%
    arrange(int_val)
  out_list <- typology_dat %>%
    ungroup() %>%
    distinct(out_val) %>%
    filter(out_val!="NA (0)") %>% 
    arrange(out_val)
  io_list <- expand.grid(int_list$int_val,out_list$out_val) %>% 
    rename(int_val=Var1,out_val=Var2)

#head(io_list)
  
  #gather data and get counts 
  io_counts <<- typology_dat %>%
    group_by(int_val, out_val) %>% 
    count() %>%
    full_join(io_list,by = c("int_val", "out_val")) %>%   # inserts missing combinations
    filter(int_val!="NA (0)" &  out_val!="NA (0)") %>% 
    mutate(n=replace_na(n,0)) %>%
    ungroup() %>% 
    mutate(int_val=factor(int_val,levels=mixedsort(int_list$int_val)))  # set int list in right order
  
  # head(io_counts)
  # nrow(int_list)*nrow(out_list)==nrow(io_counts) # quick check (should be true)
  
  #create heatmap
  heat.map <<- ggplot(data=io_counts, aes(x=int_val,y=reorder(out_val, desc(out_val)),fill=n)) +
      geom_tile(color="gray90",size=0.1) +
      geom_text(aes(label=n),show.legend = F) +
      scale_fill_gradient2(low="#f7fbff",high=high.col,name="# Cases",na.value="gray90", limits=c(0,max(io_counts$n))) +
      coord_equal() +
      # theme_tufte(base_family="Helvetica") +	# having issues with font, font colour in windows...
      theme(axis.ticks=element_line(size=0.4)) +
      theme(axis.text=element_text(size=9)) +
      theme(legend.title=element_text(size=10)) +
      theme(legend.text=element_text(size=10)) +
      theme(legend.title.align=1) +
      theme(legend.position="bottom") +
      theme(legend.key.size=unit(1, "cm")) +
      theme(legend.key.width=unit(1, "cm")) +
      #  labs(x="Conservation Intervention", y="Outcome", title ="All ecosystems") +
      theme(axis.text.x = element_text(angle=45,hjust=0,vjust=1,size=9)) +
      scale_x_discrete(position = "top") +
      scale_y_discrete(position = "right") 
  
  
}
```

# Create heat maps 
```{r eval=T}
#--- Create maps ----
# All ecosystems
my_heat_map(data_all,"Int_cat","Outcome_cat")
io_counts.all <- io_counts
(heat.map.all <- heat.map +
    labs(x="Conservation Intervention", y="Outcome", title ="All ecosystems"))
ggsave(paste0(plotdir,today.date,'_int_out_map.png'),width = 8,height = 8)

# All ecosystems - Intervention subcategory X Outcome
my_heat_map(data_all,"Intervention.subcategory", "Outcome_cat")
io_counts.subint <- io_counts
(heat.map.subint <- heat.map + labs(x="Conservation Intervention", y="Outcome", title ="All ecosystems"))
ggsave(paste0(plotdir,today.date,'_sub.int_out_map.png'),width = 16,height = 8)

# All ecosystems - Intervention  X Outcome subcategory
my_heat_map(data_all,"Int_cat", "Outcome.subcategory")
io_counts.subint <- io_counts
(heat.map.subint <- heat.map + labs(x="Conservation Intervention", y="Outcome", title ="All ecosystems"))
ggsave(paste0(plotdir,today.date,'_int_sub.out_map.png'),width = 8,height = 16)

# All ecosystems - Intervention subcategory X Outcome subcategory
my_heat_map(data_all,"Intervention.subcategory", "Outcome.subcategory")
io_counts.subintout <- io_counts
(heat.map.subint <- heat.map + labs(x="Conservation Intervention", y="Outcome", title ="All ecosystems"))
ggsave(paste0(plotdir,today.date,'_sub.int_sub.out_map.png'),width = 16,height = 12)

# Coral
my_heat_map(filter(data_all,coral==1),"Int_cat","Outcome_cat", high.col = "red3")
io_counts.coral <- io_counts
(heat.map.coral <- heat.map + labs(x="Conservation Intervention", y="Outcome", title ="Coral"))

# Mangrove
my_heat_map(filter(data_all,mangrove==1),"Int_cat","Outcome_cat", high.col = "orangered4")
io_counts.mangrove <- io_counts
(heat.map.mangrove <- heat.map + labs(x="Conservation Intervention", y="Outcome", title ="Mangrove")) 

# Seagrass
my_heat_map(filter(data_all,seagrass==1),"Int_cat","Outcome_cat", high.col = "green4")
io_counts.seagrass <- io_counts
(heat.map.seagrass <- heat.map + labs(x="Conservation Intervention", y="Outcome", title ="Seagrass")) 

# Ecosystem maps on same scale
max.val <- max(io_counts.mangrove$n,io_counts.coral$n,io_counts.seagrass$n)
plot_grid(heat.map.coral + scale_fill_gradient2(low="#f7fbff",high= "red3",name="# Cases",na.value="gray90", limits=c(0,max.val)),
          heat.map.seagrass + scale_fill_gradient2(low="#f7fbff",high= "green4",name="# Cases",na.value="gray90", limits=c(0,max.val)),
          heat.map.mangrove + scale_fill_gradient2(low="#f7fbff",high= "orangered4",name="# Cases",na.value="gray90", limits=c(0,max.val)),
          labels=letters[1:3], ncol = 3, nrow = 1, hjust=-1, align = "hv")
ggsave(paste0(plotdir,today.date,'_habitat_int_out_map.png'),width = 17,height = 8)


```

# World map
Creates a world map of 
```{r eval=T}
#---- World map ----

unique(data_all$study.ctry)
# fix data in country column
ctry.fix <- data_all %>%
  mutate(study.ctry=gsub(",",";",study.ctry),  # replace "," with ";" to help with splitting
         study.ctry=gsub("Korea; South","Korea, South",study.ctry),
         study.ctry=gsub("Turks and Caicos","Turks and Caicos Islands",study.ctry),
         study.ctry=gsub(".*Virgin Islands","U.S. Virgin Islands",study.ctry),
         study.ctry=gsub("Tanzania; United Republic Of","Tanzania, United Republic Of",study.ctry),
         study.ctry=gsub("Taiwan; Province Of China","Taiwan, Province Of China",study.ctry)) 

# all habitats
ctry.all <- ctry.fix %>% 
  group_by(aid,study.ctry) %>%
  summarise() %>% 
  filter(!is.na(study.ctry))
head(ctry.all)


# get no. articles per country (and percentage) to create vector of column names for each country by counting the number of ";" 
max.ctry <- paste0("ctry",rep(1:max(str_count(ctry.all$study.ctry, ";")+1))) 

ctry_sum <-ctry.all %>% 
  separate(study.ctry,max.ctry, sep="; ",fill="right") %>% # fill=right fills blanks with NAs
  gather("X","Country", max.ctry) %>% 
  filter(!is.na(Country)) %>% 
  select(-X) %>% 
  group_by(Country) %>% 
  count() %>% 
  mutate(pct=n/num.studies)

arrange(ctry_sum,desc(n))

# Countries that need to be fixed
ctry_sum$Country[!ctry_sum$Country%in%country$Country]
# agrep("Virgin Islands",country$Country, value = T) - search original list

# join to full country list
ctry_sum1 <- country %>% 
  left_join(ctry_sum,by="Country") %>%
  mutate(n=na.replace(n,0)) 

ctry_sum$Country[!ctry_sum$Country%in%ctry_sum1$Country] # any missing?

# plot study map
world <- ne_countries(scale = "medium", returnclass = "sf") # read in world map from rnaturalearth as sf
world.data <- world %>% 
  left_join(ctry_sum1,by=c("iso_a3"="code"))

(study_ctry_map_all <- ggplot(world.data) + 
  geom_sf(aes(fill = n)) +
#  expand_limits(x=map$long,y=map$lat) +
  theme(panel.background = element_rect(fill = "#CCCCCC", colour = "#CCCCCC"), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_fill_gradient2(low="white",mid="#2171b5",high="#08519c",
                         midpoint=max(ctry_sum1$n)/2,limits=c(0,max(ctry_sum1$n))) +
  labs(title="Study countries - all habitats"))
ggsave(paste0(plotdir,today.date,'_study_country_map.png'),width = 10,height = 5)



# -- coral 
ctry.coral <- ctry.fix %>% 
  filter(coral==1) %>% 
  group_by(aid,study.ctry) %>%
  summarise() %>% 
  filter(!is.na(study.ctry))
head(ctry.coral)


# get no. articles per country (and percentage) to create vector of column names for each country by counting the number of ";" 
max.ctry <- paste0("ctry",rep(1:max(str_count(ctry.coral$study.ctry, ";")+1))) 
num.studies <- length(unique(data_all$aid[data_all$coral==1]))

ctry_sum <-ctry.coral %>% 
  separate(study.ctry,max.ctry, sep="; ",fill="right") %>% # fill=right fills blanks with NAs
  gather("X","Country", max.ctry) %>% 
  filter(!is.na(Country)) %>% 
  select(-X) %>% 
  group_by(Country) %>% 
  count() %>% 
  mutate(pct=n/num.studies)

arrange(ctry_sum,desc(n))


# Countries that need to be fixed
ctry_sum$Country[!ctry_sum$Country%in%country$Country]
# agrep("Virgin Islands",country$Country, value = T) - search original list

# join to full country list
ctry_sum1 <- country %>% 
  left_join(ctry_sum,by="Country") %>%
  mutate(n=na.replace(n,0)) 

(study_ctry_map_coral <- ggplot() +
    geom_map(data=ctry_sum1, aes(map_id=code, fill=n),map=map) +
   # expand_limits(x=map$long,y=map$lat) +
    theme(panel.background = element_rect(fill = "#CCCCCC", colour = "#CCCCCC"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_fill_gradient2(low="white",mid="#2171b5",high="#08519c",
                         midpoint=max(ctry_sum1$n)/2,limits=c(0,max(ctry_sum1$n)))+
    labs(title="Study countries- coral"))
ggsave(paste0(plotdir,today.date,'_study_country_coral_map.png'),width = 10,height = 5)

```
# World map #2 (May 28th fixes)

LOOKS like it's supposed to, but needs to be edited to make sure that none of the data is off!!! 
May 28th Big edits.... where did they get saved??? I dont think they DID

```{r eval=T}
#---- World map #2 (May 28th fixes)----


unique(data_all$study.ctry)
# fix data in country column
ctry <- data_all %>%
  mutate(study.ctry=gsub(",",";",study.ctry),  # replace "," with ";" to help with splitting
         study.ctry=gsub("Korea; South","Korea, South",study.ctry),
         study.ctry=gsub("Turks and Caicos","Turks and Caicos Islands",study.ctry),
         study.ctry=gsub(".*Virgin Islands","U.S. Virgin Islands",study.ctry),
         study.ctry=gsub("Tanzania; United Republic Of","Tanzania, United Republic Of",study.ctry),
         study.ctry=gsub("Taiwan; Province Of China","Taiwan, Province Of China",study.ctry)) %>%
  group_by(aid,study.ctry) %>%
  summarise() %>% 
  filter(!is.na(study.ctry)) %>% 
  mutate(num.ctry=str_count(study.ctry, ";")+1)
head(ctry)


# get no. articles per country (and percentage) to create vector of column names for each country by counting the number of ";" 
max.ctry <- paste0("ctry",1:max(ctry$num.ctry)) # get vector of column names before we separate them out
num.studies <- length(unique(data_all$aid)) # number of studies in the dataset

ctry_sum <-ctry %>% 
  separate(study.ctry,max.ctry, sep="; ",fill="right") %>% # fill=right fills blanks with NAs
  gather("X","Country", max.ctry) %>%  # make all columns into one
  filter(!is.na(Country)) %>% 
  select(-X) %>% 
  group_by(Country) %>% 
  count() %>% 
  mutate(pct=n/num.studies)

arrange(ctry_sum,desc(n))

View(ctry_sum)
# Countries that need to be fixed
ctry_sum$Country[!ctry_sum$Country%in%country$Country]
# agrep("Virgin Islands",country$Country, value = T) - search original list

# join to full country list
ctry_sum1 <- country %>% 
  left_join(ctry_sum,by="Country") %>%
  mutate(n=na.replace(n,0)) 

ctry_sum$Country[!ctry_sum$Country%in%ctry_sum1$Country] # any missing?

# read in map
map <- rgdal::readOGR(paste0(mapdir,"TM_WORLD_BORDERS-0.3/TM_WORLD_BORDERS-0.3.shp"))
map <-broom::tidy(map,region="ISO3")
#map@data[map@data$NAME=="Turks and Caicos Islands",]


#plot study map
(study_ctry_map <- ggplot() +
    geom_map(data=ctry_sum1, aes(map_id=code, fill=n),map=map) +
    expand_limits(x=map$long,y=map$lat) +
    theme(panel.background = element_rect(fill = "#CCCCCC", colour = "#CCCCCC"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_fill_gradient2(low="white",mid="#2171b5",high="#08519c",
                         midpoint=max(ctry_sum1$n)/2,limits=c(0,max(ctry_sum1$n)))+
    labs(title="Study countries"))
ggsave(paste0(plotdir,today.date,'_study_country_map.png'),width = 10,height = 5)


```

# Treemapping

Outcome and Intervention tree maps

```{r eval=T}

#---- Treemapping ----
# - Outcomes
unique(data_all$Outcome.subcategory)

outcomes2 <-data_all %>% 
  filter(!is.na(Outcome.subcategory)) %>% 
  select(aid,Outcome_cat,Outcome.subcategory) %>% 
  group_by(Outcome_cat) %>% 
  mutate(out.cat=paste0(Outcome_cat,"\n (",n_distinct(aid),")")) %>% 
  group_by(Outcome_cat,Outcome.subcategory) %>% 
  mutate(n=n_distinct(aid)) %>% 
  arrange(Outcome.subcategory)
unique(outcomes2$out.cat)

pdf(file=paste0(plotdir,today.date,"_outcomes_treemap.pdf"))
treemap(outcomes2,index=c("out.cat","Outcome.subcategory"),
        vSize="n",
        type="index",
        fontsize.labels = c(15,10),
        fontcolor.labels=c("white","black"),
        fontface.labels=c(2,1),
        bg.labels=c("transparent"),
        align.labels=list(
          c("center","top"),
          c("left","bottom")
        ),
        overlap.labels=0.5,
        inflate.labels=F,
        title="Study Outcomes")
dev.off()

# - Interventions
unique(data_all$Intervention.subcategory)

intervention2 <-data_all %>% 
  filter(!is.na(Intervention.subcategory)) %>% 
  select(aid,Int_cat,Intervention.subcategory) %>% 
  group_by(Int_cat) %>% 
  mutate(int.cat=paste0(Int_cat,"\n (",n_distinct(aid),")")) %>% 
  group_by(Int_cat,Intervention.subcategory) %>% 
  mutate(n=n_distinct(aid)) %>% 
  arrange(Intervention.subcategory)

unique(intervention2$int.cat)

pdf(file=paste0(plotdir,today.date,"_intervention_treemap.pdf"))
treemap(intervention2,index=c("int.cat","Intervention.subcategory"),
        vSize="n",
        type="index",
        fontsize.labels = c(15,10),
        fontcolor.labels=c("white","black"),
        fontface.labels=c(2,1),
        bg.labels=c("transparent"),
        align.labels=list(
          c("center","top"),
          c("left","bottom")
        ),
        overlap.labels=0.5,
        inflate.labels=F,
        title="Study interventions")
dev.off()

```

# Studies over time 

```{r eval=T}

#---- Studies over time ----
All_time_gps <- data_all %>%
  group_by(Year.of.publication) %>% 
  summarise(pub.per.yr= n_distinct(aid)) %>% 
  ungroup() %>% 
  arrange(Year.of.publication) %>% 
  mutate(val=cumsum(pub.per.yr),
         gp="All") %>% 
  select(Year.of.publication,gp,val) %>% 
  filter(!is.na(Year.of.publication))
tail(All_time_gps)

# growth by decade
#overall
(max(All_time_gps$val)-min(All_time_gps$val))/(max(All_time_gps$Year.of.publication)-min(All_time_gps$Year.of.publication))
#1990s
(max(All_time_gps$val[All_time_gps$Year.of.publication<2000])-max(All_time_gps$val[All_time_gps$Year.of.publication<1990]))/10
#2000-2010
(max(All_time_gps$val[All_time_gps$Year.of.publication<2010])-max(All_time_gps$val[All_time_gps$Year.of.publication<2000]))/10
#2010-latest date (? Check this)
(max(All_time_gps$val)-max(All_time_gps$val[All_time_gps$Year.of.publication<2010]))/(max(All_time_gps$Year.of.publication)-2009)

Int_time_gps <-  data_all %>%
  group_by(Year.of.publication,Int_cat) %>% 
  summarise(int_per_yr= n_distinct(aid)) %>% 
  spread(Int_cat,value = int_per_yr) %>% 
  mutate_all(funs(replace(., is.na(.), 0))) %>% 
  ungroup() %>% 
  arrange(Year.of.publication) %>% 
  mutate_at(vars(-Year.of.publication),funs(cumsum(.))) %>% 
  gather("int_typ","val",-Year.of.publication) %>% 
  bind_rows(All_time_gps %>% rename(int_typ=gp))
tail(Int_time_gps)
# non-elegant way to convert units to factor in order to reorder plot legends
order.gp <- Int_time_gps %>% group_by(int_typ) %>% summarise(order_typ=max(val)) %>% arrange(desc(order_typ)) %>% pull(int_typ)
Int_time_gps <- Int_time_gps %>%  
  mutate(int_typ = factor(int_typ, levels = order.gp)) %>% 
  rename(Intervention=int_typ)

# int.cols <- c("black","blue","orangered1","yellow4","tan1")
# names(int.cols) <- order.gp

(pInt_time_gps <- ggplot(Int_time_gps)  + 
    geom_line(aes(x = Year.of.publication, y = val, group = Intervention, colour = Intervention), size = 1.3)  +
    ylab("Cumulative frequency") +
  #  scale_x_continuous(name="Year", breaks=seq(1985,2025,5)) +
  #  scale_colour_manual(values=int.cols) +
    ggtitle('Intervention') )
   # scale_y_continuous(limits=c(0,80), breaks=seq(0,80,10), labels=c("0","","20","","40","","60","","80")))


# Outcomes

out_time_gps <-  data_all %>%
  group_by(Year.of.publication,Outcome_cat) %>% 
  summarise(out_per_yr= n_distinct(aid)) %>% 
  spread(Outcome_cat,value = out_per_yr) %>% 
  mutate_all(funs(replace(., is.na(.), 0))) %>% 
  ungroup() %>% 
  arrange(Year.of.publication) %>% 
  mutate_at(vars(-Year.of.publication),funs(cumsum(.))) %>% 
  gather("out_typ","val",-Year.of.publication) %>% 
  bind_rows(All_time_gps %>% rename(out_typ=gp))
tail(out_time_gps)
# non-elegant way to convert units to factor in order to reorder plot legends
order.gp <- out_time_gps %>% group_by(out_typ) %>% summarise(order_typ=max(val)) %>% arrange(desc(order_typ)) %>% pull(out_typ)
out_time_gps <- out_time_gps %>%  
  mutate(out_typ = factor(out_typ, levels = order.gp)) %>% 
  rename(Outcome=out_typ)

# int.cols <- c("black","blue","orangered1","yellow4","tan1")
# names(int.cols) <- order.gp

(pout_time_gps <- ggplot(out_time_gps)  + 
    geom_line(aes(x = Year.of.publication, y = val, group = Outcome, colour = Outcome), size = 1.3)  +
    ylab("Cumulative frequency") +
    #  scale_x_continuous(name="Year", breaks=seq(1985,2025,5)) +
    #  scale_colour_manual(values=int.cols) +
    ggtitle('Outcome') )
# scale_y_continuous(limits=c(0,80), breaks=seq(0,80,10), labels=c("0","","20","","40","","60","","80")))
plot_grid(pInt_time_gps,pout_time_gps)
ggsave(paste0(plotdir,today.date,'_studies_over_time.png'),width = 12,height = 4)


```
# Stats Section
This section outputs a lot of the different stats used in the paper. Right now, I am just inputting them by hand, and so definitely would be useful to print out the stats I want to copy/paste and easy access

1. Basic Percentages
```{r eval=T}

# --- Percentages --- #
# test <-  data_all %>%
#   select(aid, Int_cat, Intervention.subcategory, Outcome_cat,Outcome.subcategory)

#Total number of studies
num.studies <- length(unique(data_all$aid))

#List of data headings
head(data_all,1)
```

2. P: Geographies

#Note: 
this code is incomplete
Need to do the "search for term within a row" method here (that we used for countries above (in the map)), and do it for all of the following rows 

For Continent percentages, I literally added up the counts and re-divided (out of 183) for percentages. very tedious
Sums: Asia (48), Oceania (40), Central America and the Caribbean (36), Africa (34), and North America (32), South America (13), Europe (6) 

For country percentages, I used the ctry_sum list, and not this

Scale of study isnt actually used in the report

Geographical scale of intervention is used


```{r eval=T}

# P: Geographies (aka intervention location)

# 1st step, clean up country columns and lists
##MAKING COUNTRY COLUMNS

#### Add country list
cty <- country$Country

# Continent
data_all %>%
  group_by(Continent) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 

# Country
data_all %>%
  group_by(study.ctry) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 
  # arrange(num)

# Scale of Study
data_all %>%
  group_by(Scale.of.study) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 

# Geographic Scale of Intervention
data_all %>%
  group_by(Geographic.scale.of.intervention) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 
##### Need to pinpoint NAs, L vs L for local

```

3. P: Habitats

```{r eval=T}

# Coral
data_all %>%
  filter(coral==1) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

# Seagrass
data_all %>%
  filter (seagrass==1) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100) 

# Mangrove
data_all %>%
  filter (mangrove==1) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100) 

# Note: these DO contain overlap, ie. some studies have multiple habitats:
data_all %>%
  group_by(Habitat.type) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num)) 

# How many studies took place in only one of three habitats?
data_all %>% 
  filter(coral + seagrass + mangrove == 1) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

# How many studies took place in multiple habitats? (2 or more)
  #doesn't inlcude "other"
data_all %>% 
  filter(coral + seagrass + mangrove >= 2) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

# How many studies took place in all 3 habitats?
data_all %>% 
  filter(coral + seagrass + mangrove == 3) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

# What are the "other" studies that don't define a habitat?
  unique(data_all$aid[data_all$Habitat.type=="Other"])
  # ONLY for the habitat types that are ONLY other, aka doesn't include 
    # studies that have a "real" habitat and an "Other"

  
```

4. I: Interventions

```{r eval=T}
  
# I: Interventions
data_all %>%
  group_by(Int_cat) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # arranges them in descending order 

  # Highest: % in cons desig and planning, species management
data_all %>%  
  filter(Int_cat== "2. Species management"| 
           Int_cat== "6. Conservation designation & planning") %>%  
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

  # Lowest: % in Enforcement and Protection, awareness raising, and 
    # Education and Training
data_all %>%  
  filter(Int_cat== "4. Enforcement & protection"| 
           Int_cat== "3. Awareness raising"| 
           Int_cat== "9. Education & training") %>%  
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

  # Subcategories (want % of each):
data_all %>%
  group_by(Intervention.subcategory) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # arranges them in descending order 
  # arrange (num) # arranges in ascending order, swap


```

5. C: Comparators, Study designs used

IN PROGRESS

# Discuss w David: what do we want from this section/how in depth?
# Still playing around

```{r eval=T}

  # Primary vs Secondary Data
data_all %>%
  group_by(Primary.or.secondary.data.) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 

  # Study Design
data_all %>%
  group_by(Study.design) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 
##### Need to do the "search for term within a row" method here

  # Type of Data
data_all %>%
  group_by(What.type.of.data.does.this.study.consider.) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 
##### Need to do the "search for term within a row" method here

  # Comparator Type
data_all %>%
  group_by(Comparator.type) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 
  # arrange (num) # for ascending order, swap
##### Need to do the "search for term within a row" method here

  # Does the Study population considers human groups?
data_all %>%
  group_by(Does.the.study.explicitly.examine.impacts.on.different.human.groups.) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
  arrange (desc(num))  # this arranges them in descending order 

#Find and look at the ONE NA Study here... what are the notes on this?
quick.stats <- data_all %>% 
         filter(is.na(Does.the.study.explicitly.examine.impacts.on.different.human.groups.))
unique(quick.stats$aid)
    # way to filter it without looking at data/one line, no quick.stats:
    # unique(data_all %>% 
      # filter(is.na(Does.the.study.explicitly.examine.impacts.on.different.human.groups.)) %>% 
      # select(aid))
    # non-piping way to do it:
      # unique(data_all$aid[is.na(data_all$Does.the.study.explicitly.examine.impacts.on.different.human.groups)])

  # Note: This 1 NA is tech number 205, so there must be a duplicate that got in
  # One section has both an N and a Y...
###########How do I ID which one has an overlap?

  # If so, what types?
  # NOT worth analysis, most of these are NAs:
    # data_all %>%
    #  group_by(If.so..what.types.of.different.groups.) %>% 
    #  summarise(num=n_distinct(aid), pct=num/num.studies*100)  %>%
    #  arrange (desc(num))  # this arranges them in descending order 

```
# Multiple Intervention Studies

#from May 28, need to go back and figure out the rest here/what exactly is going on
```{r eval=T}
(multi.int.studies <- data_all %>% 
    #   filter(Int_cat!="8. Research & monitoring") %>% 
    group_by(Year.of.publication,aid) %>% 
    summarise(n.int=n_distinct(Int_cat))
)
multi.int.aid <- multi.int.studies$aid[multi.int.studies$n.int>1]


# spot checks
table(test$n.int)
filter(test,n.int==3)
unique(data_all$Int_cat[data_all$aid==187])
data_all %>% 
  select(aid,Int_cat) %>% 
  filter(aid==187)


Multi_int_time_gps <- data_all %>%
  filter(aid%in%multi.int.aid) %>% 
  group_by(Year.of.publication) %>% 
  summarise(pub.per.yr= n_distinct(aid)) %>% 
  ungroup() %>% 
  arrange(Year.of.publication) %>% 
  mutate(val=cumsum(pub.per.yr),
         gp="Multi-intervention") %>% 
  select(Year.of.publication,gp,pub.per.yr,val) %>% 
  filter(!is.na(Year.of.publication))
View(Multi_int_time_gps)




```

6. O: Outcomes:

```{r eval=T}

data_all %>%
  group_by(Outcome_cat) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

  # % Pop/Species and Ecological Community combined (no overlaps):
data_all %>%  
  filter(Outcome_cat== "1. Population/species"| 
         Outcome_cat==  "2. Ecological community") %>%  
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

  # % in human well-being, knowledge and behavior, and governance
data_all %>%  
  filter(Outcome_cat== "5. Human well-being"| 
          Outcome_cat== "6. Knowledge and behavior"| 
          Outcome_cat== "7. Governance") %>%  
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

  # % in ecosystem function and ecosystem service
data_all %>%  
  filter(Outcome_cat== "3. Ecosystem function"| 
          Outcome_cat==  "4. Ecosystem services") %>%  
  summarise(num=n_distinct(aid), pct=num/num.studies*100)
  
  # Subcategories (want % of each):
data_all %>% 
  group_by(Outcome.subcategory) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100) %>%
  arrange (desc(num))  # this arranges them in descending order 
  # arrange (num) # for ascending order, swap
  
```

# Add eco vs soc outcome counts

This was from May 28th, but only partial, try to go back and find the rest...
```{r eval=T}
unique(data_all$Outcome_cat)
eco.outcomes <- c("2. Ecological community", "1. Population/species", "3. Ecosystem function")
soc.outcomes <- c("6. Knowledge and behavior", "5. Human well-being","7. Governance")

out.eco.v.soc <- data_all %>%
  # select(aid, Outcome_cat) %>%
  mutate(eco.out=ifelse(Outcome_cat%in%eco.outcomes,1,0),
         soc.out=ifelse(Outcome_cat%in%soc.outcomes,1,0),
         es.out=ifelse(Outcome_cat=="4. Ecosystem services",1,0)) %>% 
  group_by(aid) %>% 
  mutate(eco.out=max(eco.out),
            soc.out=max(soc.out),
            es.out=max(es.out),
            sum.out=ifelse(eco.out+soc.out>1,1,0),
            sum.es.out=ifelse(sum.out+es.out>=1,1,0)) # %>% 
 # mutate(both=ifelse(sum.out>1,"both","other"))
summary(out.eco.v.soc)

# Which outcomes most common in multi-outcome studies?
out.eco.v.soc %>%
  filter(sum.es.out==1) %>% 
  group_by(Outcome_cat) %>% 
  summarise(num=n_distinct(aid), pct=num/num.studies*100)

```


7. Time periods

IN PROGRESS

```{r eval=T}

# Extra: Time Period:

  # % of studies after 2000
  # % of studies in the year:....
  # % of studies in [specific intervention area] during [specific time]
  
  # % of studies in top 2 interventions (cons desig and spec management) 
    # during [specific time]
  
  # could do ^ for outcome, could also try to get a chart that gives # of each
    # intervention and outcome for each year. Should be able to do this!


# make barplot
test.dat <- data_all %>%
            group_by(Outcome_cat) %>% 
            summarise(num=n_distinct(aid), pct=num/num.studies)
ggplot(test.dates(Outcome_cat,num)) +
  geom_bar(stat = )
