---
title: "rudd_restoration_rscript_local"
author: "Morgan Rudd"
date: "5/5/2022"
output: html_document
---

# SETUP
Loads libraries, reads in data, cleans dataset
```{r eval=T}
pacman::p_load(rio,rgeos,treemap,gtools,cowplot,rnaturalearth,rnaturalearthdata,tidyverse, ggplot2, maptools)
today.date <- gsub("-","",Sys.Date())

#-------- Shared drive
workdir <- "R:/Gill/research/oegm/"
inputdir <- paste0(workdir,"tables/raw/")
mapdir <-  paste0(workdir,"spatial/raw/")
plotdir <- paste0(workdir,"output/restoration/")
tabledir <- paste0(workdir,"output/restoration/")

#Country data
all.ctry <- import(paste0(inputdir,"restoration/all_countries.csv"))
study.ctry <- import(paste0(inputdir,"restoration/our_countries.csv"),check.names=T) %>%  
  rename(aid=Article.ID, study.ctry=Study.Country, author.ctry=All.Author.Countries)

#WoS results
gen.comb.search <- import(paste0(inputdir,"/restoration/wos_results/combined_search.csv")) %>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs = c(0,diff(Pubs)),
         typ="combined")
gen.es.search <- import(paste0(inputdir,"/restoration/wos_results/ecoservice_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="ecosystem services")
gen.rest.search <- import(paste0(inputdir,"/restoration/wos_results/restoration_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="restoration")
#Marine WoS Term Search Results
mar.comb.search <- import(paste0(inputdir,"/restoration/wos_results/mar_combined_search.csv")) %>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="combined")
mar.es.search <- import(paste0(inputdir,"/restoration/wos_results/mar_ecoservice_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="ecosystem services")
mar.rest.search <- import(paste0(inputdir,"/restoration/wos_results/mar_restoration_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="restoration")

#Extracted Data
e.data <- import(paste0(inputdir,"/restoration/extracted_data.csv"))
es.cat <- import(paste0(inputdir, "/restoration/es_category.csv"))

#-------- Morgan
workdir <- "/Users/morganrudd/Desktop/Restoration/" #MER
inputdir <- paste0(workdir,"tables/")
mapdir <-  paste0(workdir,"spatial/")
plotdir <- paste0(workdir,"output/")
tabledir <- paste0(workdir,"output/")

#--- Organize data ----
#read in data, skip first 2 rows
# all.data<-import(paste0(inputdir,"restoration_data.xlsx"), skip =2, .name_repair = "universal") %>% 
#   mutate(Date=as.character(Date))

#Country data
all.ctry <- import(paste0(inputdir, "all_countries.csv"))
study.ctry <- import(paste0(inputdir,"our_countries.csv"),check.names=T) %>%  
  rename(aid=Article.ID, study.ctry=Study.Country, author.ctry=All.Author.Countries)

#General WoS Term Search Results
gen.comb.search <- import(paste0(inputdir,"/wos_results/combined_search.csv")) %>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="combined")
gen.es.search <- import(paste0(inputdir,"/wos_results/ecoservice_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="ecosystem services")
gen.rest.search <- import(paste0(inputdir,"/wos_results/restoration_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="restoration")

#Marine WoS Term Search Results
mar.comb.search <- import(paste0(inputdir,"/wos_results/mar_combined_search.csv")) %>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="combined")
mar.es.search <- import(paste0(inputdir,"/wos_results/mar_ecoservice_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="ecosystem services")
mar.rest.search <- import(paste0(inputdir,"/wos_results/mar_restoration_search.csv"))%>% 
  mutate(Pubs=as.integer(gsub(",","",Pubs)),
         diff.pubs =c(0,diff(Pubs)),
         typ="restoration")

#Extracted Data
e.data <- import(paste0(inputdir,"/extracted_data.csv"))
es.cat <- import(paste0(inputdir, "/es_category.csv"))
```

## ORGANIZE THE EXTRACTED DATA
```{r}
#This code selects the columns we want from data, then renames those columns we want to keep, then removes the last row of data because it's empty
new1 <- e.data%>%
  select("Article ID", "Publication Type", "Year", "Title", "Habitat", "Study Design", "Description of restoration", "ES Description", "ES Service", "Collection Method", "Economic Value?", "Value Description", "ES Data Measurement Type", "Age(yrs)", "Area(ha)")%>%
  rename(AID = "Article ID", Pub = "Publication Type", Yr = "Year", Ti = "Title", Hab = "Habitat", Design = "Study Design", Rest = "Description of restoration", ES_Desc = "ES Description", Service = "ES Service", Collect = "Collection Method", EcVal = "Economic Value?", EcVal_Desc = "Value Description", MeasTyp = "ES Data Measurement Type", Age = "Age(yrs)", Area = "Area(ha)")%>%
  left_join(es.cat, by = "Service")
```

##-----COUNTRY DATA FIGURES-----##
```{r eval=T}
# read in map
map <- rgdal::readOGR(paste0(mapdir,"TM_WORLD_BORDERS-0.3/TM_WORLD_BORDERS-0.3.shp"))
  # map <- sf::st_read(paste0(mapdir,"TM_WORLD_BORDERS-0.3/TM_WORLD_BORDERS-0.3.shp")) 
map <-broom::tidy(map,region="ISO3")

  # map <- fortify(map, region="ISO3")
#---- World map for study countries ----
unique(study.ctry$study.ctry)

# fix data in country column
ctry <- study.ctry %>% 
  mutate(study.ctry=gsub("Virgin Islands","U.S. Virgin Islands",study.ctry)) %>% 
  select(aid,study.ctry)
unique(ctry$study.ctry)

# get no. articles per country (and percentage) to create vector of column names for each country by counting the number of ";" 
max.ctry <- paste0("ctry",rep(1:max(str_count(ctry$study.ctry, ";")+1))) 
num.studies <- length(unique(ctry$aid))
ctry_sum <-ctry %>% 
  separate(study.ctry,max.ctry, sep="; ",fill="right") %>% # fill=right fills blanks with NAs
  gather("X","Country", max.ctry) %>% 
  filter(!is.na(Country)) %>% 
  select(-X)

reg.aid <- new1$AID[new1$Cat=="Regulating"] 
prov.aid <- new1$AID[new1$Cat=="Provisioning"] 
cult.aid <- new1$AID[new1$Cat=="Cultural"] 

ctry_sum_all <-ctry_sum %>% 
  group_by(Country) %>% 
  summarise(n.all=n(),pct.all=n.all/num.studies)
arrange(ctry_sum_all,desc(n.all))

ctry_sum_reg <-ctry_sum %>% 
  filter(aid%in%reg.aid) %>% 
  group_by(Country) %>% 
  summarise(n.reg=n(),pct.reg=n.reg/num.studies)

ctry_sum_prov <-ctry_sum %>% 
  filter(aid%in%prov.aid) %>% 
  group_by(Country) %>% 
  summarise(n.prov=n(),pct.prov=n.prov/num.studies)

ctry_sum_cul <-ctry_sum %>% 
  filter(aid%in%cult.aid) %>% 
  group_by(Country) %>% 
  summarise(n.cul=n(),pct.cul=n.cul/num.studies)

ctry_sum_comb <- ctry_sum_all %>% 
  left_join(ctry_sum_reg, by="Country") %>% 
  left_join(ctry_sum_prov, by="Country") %>% 
  left_join(ctry_sum_cul, by="Country")

arrange(ctry_sum_comb,desc(n))

# Countries that need to be fixed
ctry_sum_comb$Country[!ctry_sum_comb$Country%in%all.ctry$Country]

# join to full country list
ctry_sum_comb1 <- all.ctry %>% 
  left_join(ctry_sum_comb,by="Country") %>%
  mutate(across(n.all:pct.cul,~as.integer(na.replace(.,0))))
    
ctry_sum_comb$Country[!ctry_sum_comb$Country%in%ctry_sum_comb1$Country] # any missing?

#PLOT ALL STUDIES MAP
(study_ctry_map_all <- ggplot() +
    geom_map(data=ctry_sum_comb1, aes(map_id=code, fill=n.all),map=map) +
    expand_limits(x=map$long,y=map$lat) +
    theme(panel.background = element_rect(fill = "#CCCCCC", colour = "#CCCCCC"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_fill_gradient2(low="white",mid="#2171b5",high="#08519c",
                         midpoint=max(ctry_sum_comb1$n.all)/2,limits=c(0,max(ctry_sum_comb1$n.all)))+
    labs(title="Study countries - All services"))

#PLOT MAP BY ECOSYSTEM SERVICE TYPE (i.e. Regulating, Provisioning, Cultural)
(study_ctry_map_reg <- ggplot() +
    geom_map(data=ctry_sum_comb1, aes(map_id=code, fill=n.reg),map=map) +
    expand_limits(x=map$long,y=map$lat) +
    theme(panel.background = element_rect(fill = "#CCCCCC", colour = "#CCCCCC"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_fill_gradient2(low="white",mid="#2171b5",high="#08519c",
                         midpoint=max(ctry_sum_comb1$n.reg)/2,limits=c(0,max(ctry_sum_comb1$n.reg)))+
    labs(title="Study countries - reg services"))

(study_ctry_map_prov <- ggplot() +
    geom_map(data=ctry_sum_comb1, aes(map_id=code, fill=n.prov),map=map) +
    expand_limits(x=map$long,y=map$lat) +
    theme(panel.background = element_rect(fill = "#CCCCCC", colour = "#CCCCCC"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_fill_gradient2(low="white",mid="#2171b5",high="#08519c",
                         midpoint=max(ctry_sum_comb1$n.prov)/2,limits=c(0,max(ctry_sum_comb1$n.prov)))+
    labs(title="Study countries - prov services"))

(study_ctry_map_cul <- ggplot() +
    geom_map(data=ctry_sum_comb1, aes(map_id=code, fill=n.cul),map=map) +
    expand_limits(x=map$long,y=map$lat) +
    theme(panel.background = element_rect(fill = "#CCCCCC", colour = "#CCCCCC"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_fill_gradient2(low="white",mid="#2171b5",high="#08519c",
                         midpoint=max(ctry_sum_comb1$n.cul)/2,limits=c(0,max(ctry_sum_comb1$n.cul)))+
    labs(title="Study countries - cul services"))

plot_grid(study_ctry_map_all,study_ctry_map_reg,study_ctry_map_prov,study_ctry_map_cul,
          nrow=2)

ggsave(paste0(plotdir,today.date,'_study_country_map.png'),width = 20,height = 10)

# spotcheck
spotcheck.dat <- new1 %>% 
  select(AID,Cat) %>% # add whatever columns to check
  left_join(study.ctry,by=c("AID"="aid")) %>% 
  view()

```

##-----WOS DATA FIGURES-----##
# General WoS Term Search Results Over Time
```{r eval=T}
all.search <- gen.comb.search %>% 
  bind_rows(gen.es.search,gen.rest.search) %>% 
  group_by(typ) %>% 
  arrange(typ,Yr) %>% 
  mutate(cum.pubs=cumsum(Pubs))

all.search %>% 
  select(-cum.pubs) %>% 
  spread(typ,Pubs) %>% 
  head()

summary(all.search)

#PUBS OVER TIME (GENERAL)
(wos.gen.pubs <- ggplot(filter(all.search,Yr>=1990 & Yr<2021))  + 
    geom_bar(stat = "identity", aes(x = Yr, y = Pubs, fill = typ), size = 1.3, position=position_dodge())  +
    ylab("No. of Publications") +
    ggtitle('General WoS Search Results')+
  theme_classic()) 

#CUMULATIVE PUBS OVER TIME (GENERAL)
(wos.gen.cum <- ggplot(filter(all.search,Yr>=1990 & Yr<2021))  + 
    geom_line(aes(x = Yr, y = cum.pubs, group = typ, colour = typ), size = 1.3)  +
    ylab("Cumulative Frequency") +
   ggtitle('General WoS Search Results')+
  theme_classic())

#NEW PUBS OVER TIME (GENERAL) - experimental
(wos.gen.newpubs <- ggplot(filter(all.search,Yr>=1990 & Yr<2021))  + 
    geom_line(aes(x = Yr, y = diff.pubs, group = typ, colour = typ), size = 1.3)  +
    ylab("Differences in new publications per year") +
   ggtitle('General WoS Search Results')+
  theme_classic())

plot_grid(wos.gen.pubs,wos.gen.cum, nrow=1)

ggsave(paste0(plotdir,today.date,'_gen_over_time.png'),width = 15,height = 5)


???#RATE OF CHANGE IN PUBS (GENERAL)
  #rate.pubs<- diff(all.mar.search$Pubs)
#(p.wos.gen.rate <- ggplot(filter(all.search,Yr>=1990 & Yr<2021))  + 
    #geom_line(aes(x = Yr, y = cum.pubs, group = typ, colour = typ), size = 1.3)  +
   # ylab("Rate of Change") +
  # ggtitle('General WoS Search Results Over Time')+
 # theme_classic())

#ggsave(paste0(plotdir,today.date,'_rate_change_studies_over_time.png'),width = 12,height = 5)
```

# Marine WoS search results over time
```{r eval=T}
all.mar.search <- mar.comb.search %>% 
  bind_rows(mar.es.search,mar.rest.search) %>% 
  group_by(typ) %>% 
  arrange(typ,Yr) %>% 
  mutate(cum.pubs=cumsum(Pubs))

all.mar.search %>% 
  select(-cum.pubs) %>% 
  spread(typ,Pubs) %>% 
  view()

summary(all.mar.search)

#PUBS OVER TIME (MARINE)
(wos.mar.pubs <- ggplot(filter(all.mar.search,Yr>=1990 & Yr<2021))  + 
    geom_bar(stat = "identity", aes(x = Yr, y = Pubs, fill = typ), size = 1.3, position=position_dodge())  +
    ylab("No. of Publications") +
    ggtitle('Marine WoS Search Results')+
  theme_classic()) 

#CUMULATIVE PUBS OVER TIME (MARINE)
(wos.mar.cum <- ggplot(filter(all.mar.search,Yr>=1990 & Yr<2021))  + 
    geom_line(aes(x = Yr, y = cum.pubs, group = typ, colour = typ), size = 1.3)  +
    ylab("Cumulative Frequency") +
   ggtitle('Marine WoS Search Results')+
  theme_classic())

#NEW PUBS OVER TIME (GENERAL) - experimental
(wos.mar.newpubs <- ggplot(filter(all.mar.search,Yr>=1990 & Yr<2021))  + 
    geom_line(aes(x = Yr, y = Pubs, group = typ, colour = typ), size = 1.3)  +
    ylab("Differences in new publications per year") +
   ggtitle('Marine WoS Search Results')+
  theme_classic())

plot_grid(wos.mar.pubs,wos.mar.cum, nrow=1)

ggsave(paste0(plotdir,today.date,'_mar_over_time.png'),width = 15,height = 5)

???#RATE OF CHANGE IN PUBS (MARINE)

```

##-----EXTRACTED DATA FIGURES-----##
## Publications Over Time (Barplot)
```{r}
#This code selects for the article ID and publication year, then identifies distinct rows (i.e. only allowing the AID to show up once)
pub_yr <- new1%>%
  select(AID, Yr, Hab)%>%
  distinct()%%

pub_yr%>%
  count(Hab)

# Coral n=1
#Mangrove n=56
#Seagrass n=1

table(pub_yr$Yr)

# 2018 has most publications (n=10)

#Create Barplot to show # of publications over time
ggplot(pub_yr, aes(x=Yr, fill=Hab))+geom_bar()+labs(x = "Year", y = "No. Publications")+theme_classic()+theme(axis.text.x = element_text(angle = 45))+ guides(fill = guide_legend(title = "Habitat"))
  #+ scale_x_discrete(limits=c(2004:2020))
  #+ scale_y_discrete(expand = c(0,0), limits=c(0:30), breaks=seq(0, 30, by = 2))

ggsave(paste0(plotdir,today.date,'_pubs_over_time.png'),width = 10,height = 5)
```

## Ecosystem Services (Barplot)
```{r}
#This counts # of each type of service in the entire dataset; No need for "distinct" because each eco service is unique
new1%>%
  count(Service)

# Climate Regulation n = 31
# Food n = 15
# Erosion Regulation n = 13
# Natural Hazard Regulation n = 10
# Fiber, Recreation/Ecotourism, and Water Purification/Waste Treatment n = 8

new1%>%
  count(Cat)

# Cultural n= 25
# Provisioning n = 42
# Regulating n = 67

#Create Barplot to show Ecosystem Services
ggplot(new1, aes(x = fct_rev(fct_infreq(Service)), fill=Cat)) + geom_bar() + labs(x = "Ecosystem Service", y = "Count") + theme_classic() + theme(axis.line = element_line(color='black')) + scale_y_discrete(expand = c(0,0)) + coord_flip()

ggsave(paste0(plotdir,today.date,'_eco_service_barplot.png'),width = 10,height = 12)
```

## Measurement Type (Barplot)
```{r}
#Distinct rows aren't needed for this dataframe because each measurement type is tied to a unique ecosystem service outcome

new1%>%
  select(AID, Service, MeasTyp)%>%
  count(MeasTyp)
  #Environmental measurements n= 46
  #Social measurements n= 88

typ <- new1%>%
  select(AID, MeasTyp)%>%
  distinct()

table(typ$MeasTyp)
  # 41 studies used environmental data
  # 17 studies used social data

table(new1$Cat,new1$MeasTyp)
  #Cultural-- 100% Social
  #Provisioning-- ~93% Social
  #Regulating-- ~64% Environmental measures

#Create barplot to show measurement type
ggplot(new1, aes(x = (MeasTyp), fill=Cat)) + geom_bar() + labs(x = "Measurement Type", y = "Count") + theme_classic() + theme(axis.line = element_line(color='black'))

ggsave(paste0(plotdir,today.date,'_meastyp_barplot.png'),width = 10,height = 12)

#Create barplot to show measurement type
ggplot(new1, aes(x = (Cat), fill=MeasTyp)) + geom_bar() + labs(x = "Ecosystem Service Type", y = "Count") + theme_classic() + theme(axis.line = element_line(color='black'))

ggsave(paste0(plotdir,today.date,'_meastyp_barplot2.png'),width = 10,height = 12)

```


##-----DESCRIPTIVE STATISTICS-----#
## Look @ Journal Type
```{r}
new1%>%
  select(AID, Pub)%>%
  distinct()%>%
  count(Pub)

#There are 12 articles in Open Access Journals, 45 articles in Pay Journals, and 1 NA
```

## Look @ Habitat Type
```{r}
new1%>%
  select(AID, Hab)%>%
  distinct()%>%
  count(Hab)
#There is 1 coral study, 56 mangrove studies, and 1 seagrass study
```

#Size of Restoration Projects
```{r}
#This code selects for the article ID and Size of restoration project, then identifies distinct rows (i.e. only allowing the AID to show up once)
size <- new1%>%
  select(AID, Area)%>%
  distinct()

size%>%
  count(Area)
#Min area= 0.015552 ha
#Max area= 81700 ha
#30 studies included information on area restored
```

#Age of Restoration Projects
```{r}
#This selects for the article ID and Age of restoration, then identifies distinct rows (i.e. only allowing the AID to show up once), then counts the Ages
age <- new1%>%
  select(AID, Age)%>%
  distinct()

age%>%
  count(Age)

#Min age= 2.4 yrs
#Max age= 70 yrs
#51 studies included information for age of restored site
#24 study sites evaluated ages 10 yrs or younger
```

## Look at Economic Valuation
```{r}
#This code selects for the article ID, ecosystem service, and economic valuation
#Distinct rows aren't needed for this dataframe because each economic valuation is tied to a unique outcome

new1%>%
  select(AID, Service, EcVal)%>%
  count(EcVal)

#Of the 134 distinct ecosystem services reported, only 18 had associated economic values

#Identify which ecosystem services had economic values reported
ec.val <- filter(new1, EcVal == "Y")%%
  table(ec.val$Cat)
  
  #Overwhelmingly provisioning services n = 12
```